---
title: "Assignment5"
author: "Shakti Patro & Kavya Nagendrakumar"
date: "March 09, 2016"
output: pdf_document
---
## Authors : Shakti Patro, Kavya Nagendrakumar


## Description:
This assignment's objective was to compute missed connections for all two-hop paths. Fro this we calculated the total nummber of connections and missed connections for a each carrier for each year. This assigment 


## Code Analysis
 
In this assignemnt, we learnt to use WholeFileInputFormat, which is used to load the whole file as a input split.
This was very helpful in the scenario as we were able to do most of our calculations in the mapper and reducer load was drastically decreased. Following are the important bullets in our code design.

1. As we knew that each file was a month's data, so we decided to use the WholeFileInputFormat. We had to implement the Format class and a reader class for this. Also we had to use Buffered stream reader to read the whole file as bytes. This helped to read each line of data.

2. In the mapper, we used a Map to store the values , key is CompositeKey(carrier, year) and value is compositeKey(carrier,year,  cancelled, connections, missedConnections, actual, scheduled, isArriving, airport). After aggregating all file data , we used two for loops to iterate over data and calculate connections and missed connections.

3. For handling the month rollover, we had to send all data which were in the 6 hours range in the last day of month for arriving flights and first day of month for departing flights.

4. The reducer calculates the monthly rollover and aggregates with the connections for a carrier and year.

## Device Properties

__LOCAL__ :

OS        : MacBook Pro (Retina, 13-inch, Early 2015) 

Processor : 2.7 GHz Intel Core i5

Memeory   : 8 GB 1867 MHz DDR3

__AWS__ :

Instance Count = 11(1 Master , 10 Slaves)

Master Instance Type = m3.xlarge

Slave Instance Type = m3.xlarge


## Runs and Outputs

__On Cluster (25 Files)__ : 

Time Taken :

Run 1:    15.7 min

Run 2:    7min

__On Cluster (336 Files)__ :

Time Taken : 9min


## Plots:

__(using 336 files data)__

* Plot 1 shows the number of connections for each Carrier 

* Plot 2 shows missed connections for each carrier per year.

```{r, echo=FALSE}
options( warn = -1 )
suppressMessages(require("plyr"))
suppressMessages(require("dplyr"))
suppressMessages(require("ggplot2"))
suppressMessages(require("reshape2"))

s<- read.delim(file = "output/all_files_336", sep = "\t", col.names = c("Carrier", "Year", "Connections", "Missed"))
s["Year2"] <- as.Date(paste(s$Year,"-01-01",sep=""))
qplot(Year2, log(Connections), data = s, colour = Carrier, geom = "line", position = "stack")

qplot(Year2, log(Missed), data = s, colour = Carrier, geom = "line", position = "stack")

```

\pagebreak

* Plot 3 shows missed connection rate for all carriers. The larger bubbles show larger missed connection for carrier.

```{r, echo=FALSE}
ggplot(s, aes(as.factor(Year), as.factor(Carrier))) + geom_point(aes(size = log(Missed))) + ggtitle("Figure 3: Missed rate of Carriers")

```

\pagebreak

### Data: (For 25 Files)
Carrier | 		YEAR  | Connections   | Missed Connections 
------- | --------- | ------------- | ------------------
AA		  |		2015		|		1781027			|		67315
B6	  	|		2015		|		2017887			|		78178
UA		  |		2015		|		2829106			|		109938
AA		  |		2014		|		23622025		|		884784
B6		  |		2014		|		26538414		|		1020237
UA		  |		2014		|		37945479		|		1522214
DL	  	|		2013		|		43072219		|		1319285
VX		  |		2013		|		43418895		|		1331841
DL		  |		2014		|		48910845		|		1384028
EV		  |		2013		|		68282609		|		2327700
NK		  |		2015		|		68317678		|		2329623
VX		  |		2014		|		68669818		|		2342341
WN		  |		2013		|		96081937		|		3112888
YV		  |		2013		|		97435843		|		3174420
9E		  |		2013		|		6115190			|		226149
DL		  |		2015		|		9976851			|		321519
EV		  |		2014		|		25463846		|		1137540
FL		  |		2013		|		28141530		|		1265406
VX		  |		2015		|		28167467		|		1266186
WN		  |		2014		|		56870685		|		2219372
EV		  |		2015		|		984590			|		48291
F9		  |		2013		|		2067725			|		95425
FL		  |		2014		|		2944461			|		125886
HA		  |		2013		|		3954681			|		152731
WN		  |		2015		|		6342134			|		222086
AS		  |		2013		|		1626305			|		54482
F9		  |		2014		|		2653241			|		109023
HA		  |		2014		|		3710768			|		141629
MQ		  |		2013		|		15555241		|		703877
OO		  |		2013		|		28038139		|		1278960
US		  |		2013		|		40221204		|		1633161
AS		  |		2014		|		1756888			|		68926
F9		  |		2015		|		1795915			|		71458
HA		  |		2015		|		1887598			|		74837
MQ		  |		2014		|		11285367		|		551369
OO		  |		2014		|		22768926		|		1125520
US		  |		2014		|		34844551		|		1491402
AA		  |		2013		|		23184019		|		716082
AS		  |		2015		|		23321263		|		721395
B6		  |		2013		|		26121219		|		859997
MQ		  |		2015		|		26834390		|		898859
OO		  |		2015		|		27658475		|		947767
UA		  |		2013		|		39467666		|		1436218
US		  |		2015		|		40419755		|		1467149

\pagebreak

### Data: (For 336 Files)

Carrier | 		YEAR  | Connections   | Missed Connections 
------- | --------- | ------------- | ------------------
AA		  |		2014		|		23622025		|		884784
B6		  |		2014		|		26538414		|		1020237
UA	  	|		2014		|		37945479		|		1522214
AA	  	|		2015		|		1781027		  |		67315
B6		  |		2015		|		2017887		  |		78178
UA		  |		2015		|		2829106		  |		109938
DL		  |		2013		|		43072219		|		1319285
VX		  |		2013		|		43418895		|		1331841
DL		  |		2014		|		48910845		|		1384028
EV		  |		2013		|		68282609		|		2327700
NK		  |		2015		|		68317678		|		2329623
VX		  |		2014		|		68669818		|		2342341
WN		  |		2013		|		96081937		|		3112888
YV		  |		2013		|		97435843		|		3174420
9E	  	|		2013		|		6115190		  |		226149
DL		  |		2015		|		9976851		  |		321519
EV		  |		2014		|		25463846		|		1137540
FL		  |		2013		|		28141530		|		1265406
VX		  |		2015		|		28167467		|		1266186
WN		  |		2014		|		56870685		|		2219372
EV		  |		2015		|		984590		  |		48291
F9		  |		2013		|		2067725		  |		95425
FL		  |		2014		|		2944461		  |		125886
HA		  |		2013		|		3954681		  |		152731
WN		  |		2015		|		6342134		  |		222086
AS		  |		2013		|		1626305		  |		54482
F9		  |		2014		|		2653241		  |		109023
HA		  |		2014		|		3710768		  |		141629
MQ		  |		2013		|		15555241		|		703877
OO		  |		2013		|		28038139		|		1278960
US		  |		2013		|		40221204		|		1633161
AS		  |		2014		|		1756888	  	|		68926
F9		  |		2015		|		1795915	  	|		71458
HA		  |		2015		|		1887598		  |		74837
MQ		  |		2014		|		11285367		|		551369
OO		  |		2014		|		22768926		|		1125520
US		  |		2014		|		34844551		|		1491402
AA		  |		2013		|		23184019		|		716082
AS		  |		2015		|		23321263		|		721395
B6		  |		2013		|		26121219		|		859997
MQ		  |		2015		|		26834390		|		898859
OO		  |		2015		|		27658475		|		947767
UA		  |		2013		|		39467666		|		1436218
US		  |		2015		|		40419755		|		1467149

